\huge A Usability Evaluation of Tor Launcher

### 2017-03-14 pets2017-paper/pets2017-paper.tex
Add my funding sources.

\section {Acknowledgments}
We would like to thank the peer reviewers, especially our shepherd Jens Grossklas, for giving us valuable feedback on this paper. Tor Project employees Georg Koppen, Mike Perry, and Isabela Bagueros provided valuable insights about the history of Tor launcher and internal constraints. This work was done in collaboration with Xlab (Experimental Social Science Laboratory)~\cite{xlab}, SCRUB (secure computing research for users' benefit)~\cite{scrub}, and BLUES (Berkeley laboratory for usable and experimental security)~\cite{blues} laboratories, with funding from Intel and the National Science Foundation.

>>>>

\section {Acknowledgments}
We would like to thank the peer reviewers, especially our shepherd Jens Grossklas, for giving us valuable feedback on this paper. Tor Project employees Georg Koppen, Mike Perry, and Isabela Bagueros provided valuable insights about the history of Tor launcher and internal constraints. This work was done in collaboration with Xlab (Experimental Social Science Laboratory)~\cite{xlab}, SCRUB (secure computing research for users' benefit)~\cite{scrub}, and BLUES (Berkeley laboratory for usable and experimental security)~\cite{blues} laboratories, with support from
Intel, the National Science Foundation,
the Open Technology Fund through the Freedom2Connect Foundation, and from
the US Department of State, Bureau of Democracy, Human Rights and Labor.
